---
title: "Table column names"
description: Get the names of the columns from each table within a table, taken from MySQL tables within the database 'wfp'.
---

<!-- Targets -->
* Join tables per following traits
    `Nutrition Requirements per populace per country`
    [x]1.Nutrition = Nutrition per commodity
    [x]2.Landuse   = Commodity quantity per arable land per country
    [x]3.Trade     = Commodity exported/imported per country
    [x]4.Products  = Commodity grown per country
    [x]5.Currency  = Exchange prices per country
    [x]6.Price     = Commodity prices per country
                                      per market
                     Living wages per person per country
                                  per market
* List names per dataset


```{r, message=FALSE}
library(DBI)
library(tidyverse)
con <- dbConnect(RMariaDB::MariaDB(), user = "mysql", password = "password", dbname = "wfp")
# Get tables from 'wfp'
tables <- data.frame(dbListTables(con), stringsAsFactors = F)
fields <- list()
# tables.fields <- tibble()
for(i in c(1:length(tables$dbListTables.con.))){
  fields <- rbind(fields, list(dbListFields(con, tables$dbListTables.con.[i])))
  }
dbDisconnect(con)
table.fields <- tibble(); for(i in 1:12){
  table.fields <- rbind(as.list(table.fields), list(c(tables[[1]][i], fields[[i]])))
}
rm(con, fields, tables, i)

# Function is run twice as multiple required to meet matching lengths
for(i in 1:12){
  if(length(table.fields[[i]]) < 13){
    table.fields[[i]] <- c(table.fields[[i]], NA)}}

table.fields <- unname(data.frame(lapply(table.fields, unlist), stringsAsFactors = F))

```

```{r}
Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
table.fields$common <- apply(table.fields, 1, Mode)
table.fields[1,13] <- "Common"
colnames(table.fields) <- table.fields[1,]
table.fields <- table.fields[-1,]

for(i in 1:12){
  for(j in 1:12){
    if(identical(table.fields[i,j],table.fields[i,"Common"])){
      table.fields[i,j] <- NA
    }
  }
}
```

```{r}
con <- dbConnect(RMariaDB::MariaDB(), user = "mysql", password = "password", dbname = "wfp")


dbDisconnect(con)
```

