---
title: "WFP ETL - Old"
description: Initial level WFP ETL. Issues include - 
                dataset download from hdx repo instead of FAO, 
                changed column names to local personalized names which are no longer matchable with other tables,
                drops columns with id levels, 
                dates are changed to lubridate attributes, 
                limited to saving rds file and not creating MySQL table.
---

Download latest WFP dataset

```{r, include=FALSE}
library(rhdx)
library(tidyverse)
set_rhdx_config(hdx_site = "prod")
```

Download and read hdx dataset into R
```{r}
wfp <- pull_dataset("wfp-food-prices") %>% 
  get_resource(index = 1) %>% 
  read_resource(wfp, folder = getwd())
```

```{r, wfp_ETL}
wfp <- wfp %>% select("adm0_name","adm1_name","mkt_name","cm_name","cur_name","pt_name","um_name","mp_month","mp_year","mp_price")
names(wfp) <- c("country", "state", "market", "commodity", "currency", "partner", "unit", "month", "year", "price")
wfp$time <- lubridate::period(years = wfp$year, months = as.numeric(wfp$month))
wfp$month <- NULL
wfp$year <- NULL
wfp$price <- as.numeric(wfp$price)
```

Create `Currency` multiplier 
Create `Units` multiplier, then NLP

#Multipliers 
#Time wfp$time to curr$date for month-year along with 
#Currency name matching (colnames(curr)) with wfp$currency

Up-to-date currency conversion table can be found via HDX-https://data.humdata.org/dataset/ecb-fx-rates

```{r, Get_currency_table}
# Currently only 32 currencies available via this dataset

# pull_dataset("ecb-fx-rates") %>%
# get_resource(index = 1) %>%
# download_resource(folder = "/home/agar/Documents/WFP")
# curr_table <- read_csv("/home/agar/Documents/WFP/ECB_FX_USD-quote.csv", col_names = F)
# curr_table <- curr_table[-2,]
```


```{r, currency multiplier}
curr <- data.frame(
          t(
            read_csv("~/Documents/WFP/Dataset/Currency/Currency data.csv", col_names = FALSE, skip = 1)), stringsAsFactors = F)

curr$X1 <- as.character(unlist(data.frame(strsplit(curr$X1, "[.]"))[3,]))
curr$X3 <- NULL
curr$X4 <- NULL

rownames(curr) <- c("date", curr[c(2:41),1])
curr$X1 <- NULL
curr$X2 <- NULL
curr <- data.frame(t(curr), stringsAsFactors = F)

#Convert 2020Jan to lubridate::period using year and month
date_curr <- data.frame(
  "month" = unlist(data.frame(lapply(curr$date, strsplit, "[[:digit:]]"))[5,]), 
  "year" = unlist(data.frame(lapply(curr$date, strsplit, "[[:alpha:]]"))[1,]) 
  )
date_curr$month <- match(as.character(date_curr$month), month.abb)
date_curr$year <- as.numeric(as.character(date_curr$year))
curr$date <- lubridate::period(years = date_curr$year, months = date_curr$month)
rm(date_curr)
curr <- pivot_longer(curr, -"date")
curr <- curr[complete.cases(curr),]
#Created currency list multiplier by date and currency
```

# Convert units via multiplier

```{r, unit}
unit <- sort(unique(wfp$unit))
unit2 <- sort(unique(wfp$unit)) %>% 
  strsplit(c(" ")) %>%  
  as.data.frame()
# Issue of 1x (non-numerical) units with spaces appear, although "cubic meter" is the only observed case
# Issue2 of 1x (non-numerical) units with "/" appear, with additional number
unit2[] <- lapply(unit2, as.character)
unit2 <- as.data.frame(t(unit2), stringsAsFactors = F)
unit <- data_frame("main" = unit, "multi" = unit2$V1, "unit" = unit2$V2)
rm(unit2)
# Add 1x to no numerical multipliers
unit[grepl("[a-zA-z]", unit$multi), "multi"] <- 1
```

```{r}
# Determine from unit$unit[i] >= unique(wfp$unit) == unit$unit[i]
# Number of different commodidities per unit$main
for(i in c(1:length(unit$main))){
    unit[i,"comm_num"] <- length(unique(wfp$commodity[unit$main[i] == wfp$unit]))
}
unit$multi <- as.numeric(unit$multi)

```

*LCU=Local Currency Unit
**Marmite=2.7kg
***MT=1000kg
****Libra(Pound)=0.45359237kg
*****Cuartilla=2.875575kg

# Modify unit$multi and unit$unit per below:
KG <- KG, Pounds, G, Pound, LCU/3.5kg, Marmite**, MT*** , Libra**** , Cuartilla*****
  Pounds, Pound, Libra**** = 0.45359237kg
  G = 0.001kg
  LCU/3.5kg = 3.5kg
  Marmite** = 2.7kg
  MT*** = 1000kg 
  Cuartilla***** = 2.875575kg
L <- L, ML, Gallon
  ML = 0.001L
  Gallon = 3.78541L
pcs <- pcs, Tubers, Bar, Brush, Bunch, Course, Cylinder, Dozen, Head, Loaf, Package, Packet, Sack, Unit
  Dozen = 12 pcs
Currency_exchange <- USD/LCU
special <- Day, kWh, Month, meter
  month = 30.42Day
  

```{r, unit multiplier table}

#run 1st level multiplier for kg, L, pcs, etc
# KG <- Pounds, G, Pound, LCU/3.5kg, Marmite**, MT*** , Libra**** , Cuartilla*****
#   Pounds, Pound, Libra**** = 0.45359237kg
#   G = 0.001kg
#   LCU/3.5kg = 3.5kg
#   Marmite** = 2.7kg
#   MT*** = 1000kg 
#   Cuartilla***** = 2.875575kg

for(i in c(1:length(unit$main))){
  if(any(unit$unit[i]==c("Pounds","Pound","Libra"))){
    unit$multi[i] <- unit$multi[i]*0.45359237
  } 
  if(unit$unit[i]=="LCU/3.5kg"){
    unit$multi[i] <- unit$multi[i]*3.5
  }
  if(unit$unit[i]=="G"){
    unit$multi[i] <- unit$multi[i]*0.001
  }
  if(unit$unit[i]=="Marmite"){
    unit$multi[i] <- unit$multi[i]*2.7
  }  
  if(unit$unit[i]=="MT"){
    unit$multi[i] <- unit$multi[i]*1000
  }  
  if(unit$unit[i]=="Cuartilla"){
    unit$multi[i] <- unit$multi[i]*2.875575
  }
# L <- L, ML, Gallon
#   ML = 0.001L
#   Gallon = 3.78541L
  if(unit$unit[i]=="ML"){
    unit$multi[i] <- unit$multi[i]*0.001
  }
  if(unit$unit[i]=="Gallon"){
    unit$multi[i] <- unit$multi[i]*3.78541
  }
# pcs <- pcs, Tubers, Bar, Brush, Bunch, Course, Cylinder, Dozen, Head, Loaf, Package, Packet, Sack, Unit
#   Dozen = 12 pcs
  if(unit$unit[i]=="Dozen"){
    unit$multi[i] <- unit$multi[i]*12
  }
# special <- Day, kWh, Month, meter
#   month = 30.42Day (avg per year)
  if(unit$unit[i]=="Month"){
    unit$multi[i] <- unit$multi[i]*30.42
  }  
}  
for(i in c(1:length(unit$main))){
  if(any(unit$unit[i]==c("Pounds", "G", "Pound", "LCU/3.5kg", "Marmite", "MT", "Libra", "Cuartilla"))){
    unit$unit[i] <- "KG"
   }
  if(any(unit$unit[i]==c("ML", "Gallon"))){
    unit$unit[i] <- "L"
   }
  if(any(unit$unit[i]==c("Tubers", "Bar", "Brush", "Bunch", "Course", "Cylinder", "Dozen", "Head", "Loaf", "Package", "Packet", "Sack", "Unit"))){
    unit$unit[i] <- "pcs"
   }
  if(any(unit$unit[i]=="Month")){
    unit$unit[i] <- "Day"
   }
}
```

<!-- Sub for price_multiplier unit$multi to wfp$price per wfp$unit -->
<!-- Sub for unit_multiplier unit$unit to wfp$unit -->

```{r}
for(i in c(1:length(unit$unit))){
  wfp$price <- gsub(unit$main[i], unit$multi[i], wfp$price)
  wfp$unit <- gsub(unit$main[i], unit$unit[i], wfp$unit)
}
wfp$unit <- gsub("1KG", "KG", wfp$unit)
wfp$price <- as.numeric(wfp$price)
rm(unit)
```

```{r}
# write_rds(wfp, "/home/agar/Documents/WFP/WFP")
# wfp <- as_tibble(read_rds("/home/agar/Documents/WFP/WFP"))
```

Convert currency units into wfp
```{r}
# x <- c(unique(curr$name), 
#        unique(wfp$currency))
# sort(unname(unlist(unique(curr_table[1,-1]))))
# sort(unique(x))
```

wfp$commodity 
```{r}
# split <- gsub(" - Retail", "", wfp$commodity) 
# split <- gsub(" - Wholesale", "", split) %>% 
#   unique() %>%  unlist()
# split <- gsub("[)]", "", split) 
# split <- strsplit(split, "[(]")
# split <- t(as.data.frame(split, stringsAsFactors = F, col.names = 1:236, row.names = c("commodity", "comment")))
# for(i in c(1:length(split[,1]))){
#   if(split[i,1]==split[i,2]){
#     split[i,2] <- NA
#     }
# }
# split <- data.frame(split, stringsAsFactors = F)
```

```{r}
wfp$commodity <- gsub(" - Retail", "", wfp$commodity) 
wfp$commodity <- gsub(" - Wholesale", "", wfp$commodity)

wfp$commodity <- gsub("[)]", "", wfp$commodity) 
wfp <- wfp %>% separate(commodity, c("commodity", "commodity_2"), "[(]")
wfp$commodity <- trimws(wfp$commodity, "right")
wfp$commodity_2 <- trimws(wfp$commodity_2, "both")

write_rds(wfp, "/home/agar/Documents/WFP/WFP")

# unique(wfp$currency[wfp$commodity=="Exchange rate"])
# 
# sort(unique(wfp$commodity))
# sort(unique(wfp$currency))
# sort(unique(curr$name))
```

